\section{System Model}\label{sec:system_model}

\subsection{Geometry and Region of Interest}
Let $\mathbf{x} = [e, n]^{\top}$ denote the unknown terminal easting-northing (EN)
offset in meters from a known reference point within a bounded region of interest
$\mathcal{R} \subset \mathbb{R}^2$.  The terminal altitude is assumed fixed or
obtained from a coarse DEM; only the horizontal position is estimated in this
work.

The terminal position in ECEF coordinates is
\begin{equation}
  \mathbf{p}_t(\mathbf{x}) = \mathbf{p}_0 + \mathbf{R}_{\text{ENU}} \begin{bmatrix} e \\ n \\ 0 \end{bmatrix},
  \label{eq:terminal_ecef}
\end{equation}
where $\mathbf{p}_0$ is the ECEF position of the reference point and
$\mathbf{R}_{\text{ENU}}$ is the rotation matrix from local ENU to ECEF.

\subsection{Satellite State from TLE/SGP4}
A ground station acquires a two-line element (TLE) set for the visible LEO
satellite.  The SGP4 propagator~\cite{todo_sgp4} returns the satellite position
$\mathbf{s}(t) \in \mathbb{R}^3$ (km, ECEF) and velocity
$\mathbf{v}_s(t) \in \mathbb{R}^3$ (km/s, ECEF) at UTC time $t$.  The resulting
trajectory defines the geometric basis for all Doppler and delay computations.

\subsection{Range, Range-Rate, and LOS Vector}
The geometric range at time $t$ is
\begin{equation}
  \rho(t; \mathbf{x}) = \bigl\|\mathbf{s}(t) - \mathbf{p}_t(\mathbf{x})\bigr\|_2 .
  \label{eq:range}
\end{equation}
The line-of-sight (LOS) unit vector from terminal to satellite is
\begin{equation}
  \mathbf{u}(t; \mathbf{x}) = \frac{\mathbf{s}(t) - \mathbf{p}_t(\mathbf{x})}
                                   {\rho(t; \mathbf{x})} .
  \label{eq:los_unit}
\end{equation}
Assuming the terminal is stationary or slowly moving during one pass
($\|\mathbf{v}_t\| \ll \|\mathbf{v}_s\|$), the scalar range-rate is
\begin{equation}
  \dot{\rho}(t; \mathbf{x})
  = \mathbf{u}(t; \mathbf{x})^\top \mathbf{v}_s(t)
  = \frac{(\mathbf{s}(t) - \mathbf{p}_t)^\top \mathbf{v}_s(t)}
          {\rho(t; \mathbf{x})} .
  \label{eq:range_rate}
\end{equation}

\subsection{Doppler Observation}
The one-way Doppler shift at carrier frequency $f_c$ is
\begin{equation}
  f_D(t; \mathbf{x}) = -\frac{f_c}{c}\,\dot{\rho}(t; \mathbf{x}),
  \label{eq:doppler}
\end{equation}
where $c = 299\,792.458$ km/s.  The terminal's low-cost oscillator introduces
a constant carrier frequency offset $b_0$ (Hz), a linear drift term $b_1$ (Hz/s),
and zero-mean Gaussian noise $\epsilon_i \sim \mathcal{N}(0, \sigma_f^2)$.

At discrete observation time $t_i = t_0 + i\Delta t_{\text{pkt}}$ the received
frequency is
\begin{equation}
  y_f(t_i) = f_D(t_i; \mathbf{x}) + b_0 + b_1\,t_i + \epsilon_i .
  \label{eq:freq_obs}
\end{equation}

\subsection{Optional Delay Observation}
When packet arrival timestamps are recorded, the propagation delay
$\tau(t) = \rho(t; \mathbf{x})/c$ is observable up to an unknown time offset
$\Delta t$ and noise $\eta_i \sim \mathcal{N}(0, \sigma_\tau^2)$:
\begin{equation}
  y_\tau(t_i) = t_i + \Delta t + \frac{\rho(t_i; \mathbf{x})}{c} + \eta_i .
  \label{eq:delay_obs}
\end{equation}
Low-cost IEEE 802.15.4 or LoRa receivers typically have timestamp resolution
of the order of microseconds to milliseconds; the estimator models this via
$\sigma_\tau$.

\subsection{Nuisance Parameter Vector}
The unknown parameters
\begin{equation}
  \boldsymbol{\theta} = [\Delta t,\; b_0,\; b_1]^{\top}
  \label{eq:nuisance_vec}
\end{equation}
are treated as nuisance and handled jointly with position.

\subsection{Assumptions and Scope}
The current implementation and evaluation assume:
\begin{itemize}
  \item A bounded ROI is \emph{a priori} known (e.g., from network coverage
        area, cell-ID, or approximate GNSS), enabling a gridded search over
        candidate positions.
  \item The terminal is stationary or has negligible velocity during the
        observation window (approximately 5--10 minutes).
  \item TLE data for the satellite in view is available and within SGP4
        validity (typically valid to a few days).
  \item Observations are synthetic or extracted from offline IQ captures;
        no real satellite over-the-air validation is claimed in this draft.
  \item This work does not provide meter-level localization; it targets
        coarse estimation sufficient to support uplink scheduling and
        link adaptation in NTN/D2S scenarios.
\end{itemize}
Table~\ref{tab:params} summarizes the model parameters.

\begin{table}[h]
  \caption{Nuisance and State Parameters}
  \label{tab:params}
  \centering
  \begin{tabular}{cll}
    \hline
    Symbol & Description & Units \\ \hline
    $\mathbf{x}$ & Terminal EN offset (unknown) & m \\
    $\Delta t$   & Timing offset (unknown) & s \\
    $b_0$        & Constant CFO (unknown)    & Hz \\
    $b_1$        & Linear drift (unknown)    & Hz/s \\
    $\epsilon$   & Frequency noise           & Hz \\
    $\eta$       & Delay noise              & s \\ \hline
  \end{tabular}
\end{table}