\section{Bayesian Grid Posterior Estimator}\label{sec:estimator}

\subsection{Candidate Grid}
The estimator operates over a discrete grid $\mathcal{G} = \{\mathbf{x}_k\}_{k=1}^{K}$
covering the bounded ROI with uniform spacing $\Delta_g$ (meters).  The grid
resolution trades off computational cost against quantization error; a coarser
grid is used for initial survey and a finer grid for local refinement around the
MAP estimate.

\subsection{Likelihood Model}
For candidate $\mathbf{x}_k$ and nuisance vector $\boldsymbol{\theta}$, the
observation model is
\begin{subequations}
\begin{align}
  y_f(t_i) &= f_D(t_i; \mathbf{x}_k) + b_0 + b_1 t_i + \epsilon_i,
             \quad \epsilon_i \sim \mathcal{N}(0, \sigma_f^2) \\
  y_\tau(t_i) &= t_i + \Delta t + \frac{\rho(t_i; \mathbf{x}_k)}{c} + \eta_i,
                \quad \eta_i \sim \mathcal{N}(0, \sigma_\tau^2) .
\end{align}
\end{subequations}
Assuming independence across epochs and noise channels, the negative log-likelihood
(up to an additive constant) is
\begin{equation}
  \mathcal{L}(\mathbf{x}_k, \boldsymbol{\theta})
  = \frac{1}{2\sigma_f^2}\sum_{i=1}^{N}
      \bigl[y_f(t_i) - f_D(t_i; \mathbf{x}_k) - b_0 - b_1 t_i\bigr]^2
  + \frac{1}{2\sigma_\tau^2}\sum_{i=1}^{N}
      \bigl[y_\tau(t_i) - t_i - \Delta t - \rho(t_i; \mathbf{x}_k)/c\bigr]^2 .
  \label{eq:negloglik}
\end{equation}
Weak Gaussian priors on the nuisance parameters provide regularization:
$\mathcal{R}(\boldsymbol{\theta}) =
 \frac{(b_0-\mu_{b_0})^2}{2\sigma_{b_0}^2}
+\frac{(b_1-\mu_{b_1})^2}{2\sigma_{b_1}^2}
+\frac{(\Delta t-\mu_{\Delta t})^2}{2\sigma_{\Delta t}^2}$.

The full score function is $S(\mathbf{x}_k, \boldsymbol{\theta})
   = \mathcal{L}(\mathbf{x}_k, \boldsymbol{\theta}) + \mathcal{R}(\boldsymbol{\theta})$.

\subsection{Nuisance Fitting and Marginalization}
For fixed $\mathbf{x}_k$ and $\Delta t$, the frequency residuals are linear in
$b_0$ and $b_1$, admitting a weighted least-squares solution:
\begin{equation}
  \begin{bmatrix} \hat{b}_0 \\ \hat{b}_1 \end{bmatrix}
  = \arg\min_{b_0,b_1}
    \Bigl\|\mathbf{A}\begin{bmatrix}b_0\\b_1\end{bmatrix}
    - (\mathbf{y}_f - \mathbf{f}_D(\mathbf{x}_k))\Bigr\|_{\mathbf{W}}^2 ,
\end{equation}
where $\mathbf{A} = [1, \mathbf{t}]$ and $\mathbf{W} = \operatorname{diag}(1/\sigma_f^2)$.
After substituting $\hat{b}_0, \hat{b}_1$ back, the residual score is minimized
over $\Delta t$ by a one-dimensional search over the delta-t grid.

The implementation supports two modes:
\begin{itemize}
  \item \textbf{Fitting mode}: $\hat{\boldsymbol{\theta}} = \arg\min_{\boldsymbol{\theta}}
        S(\mathbf{x}_k, \boldsymbol{\theta})$; the score at the optimum is used.
  \item \textbf{Marginalization mode}: the posterior is computed as
        $p(\mathbf{x}_k|\mathbf{y}) \propto \sum_j \exp(-S(\mathbf{x}_k, \boldsymbol{\theta}_j))$
        over the $\Delta t$ grid, effectively marginalizing over time offset.
\end{itemize}

\subsection{Posterior, MAP, and Credible Region}
The unnormalized posterior for grid cell $k$ is
\begin{equation}
  p_k \propto \exp\!\bigl(-\min_{\boldsymbol{\theta}} S(\mathbf{x}_k, \boldsymbol{\theta})\bigr) .
\end{equation}
Normalizing gives
\begin{equation}
  \Pr(\mathbf{x}_k \mid \mathbf{y})
  = \frac{p_k}{\sum_{j=1}^{K} p_j} ,
  \qquad
  \sum_{k=1}^{K} \Pr(\mathbf{x}_k \mid \mathbf{y}) = 1 .
  \label{eq:posterior}
\end{equation}
The MAP estimate is
\begin{equation}
  \hat{\mathbf{x}} = \arg\max_{\mathbf{x}_k \in \mathcal{G}} \Pr(\mathbf{x}_k \mid \mathbf{y}) .
  \label{eq:map_estimate}
\end{equation}
The 95\% highest posterior density (HPD) region is the smallest set of
grid cells whose total posterior mass is at least 0.95.  The number of cells
in the HPD region and the posterior entropy serve as ambiguity diagnostics:
a large HPD or high entropy indicates that the observations do not strongly
constrain the location.

\subsection{Implementation}
The estimator is implemented in \texttt{src/leodtf/estimator\_grid\_map.py}.
Grid search over $K \times N_{\Delta t}$ candidates is embarrassingly parallel
and scales as $O(K N_{\Delta t} N_{\text{obs}})$.  Numerical stability is
maintained via log-sum-exp tricks for the posterior normalization.  The output
for each run includes: MAP EN offset, posterior grid, posterior entropy,
HPD cell count, and ambiguity score.  These diagnostics are exported to
JSON/CSV by the evaluation scripts for reproducibility.

\textbf{Disclaimer:} The current estimator performance in simulation reflects
the quality of the synthetic geometry and noise models.  Achieved accuracy
in hardware-in-the-loop and field settings has not yet been characterized.