\section{Evaluation}\label{sec:evaluation}

All evaluations to date are \textbf{synthetic and trace-driven}.
No real satellite OTA data is used.  Results are reproducible by running the
scripts listed below.  No paper performance claims are made from these runs.

\subsection{Reproducible Synthetic Pass}
The \texttt{generate\_synthetic\_dataset.py} script produces a deterministic
synthetic satellite pass (400~km altitude, 53° inclination, 10-minute duration)
and exports geometry and observations to:
\begin{itemize}
  \item \texttt{experiments/results/synthetic/synthetic\_pass\_dataset.json}
  \item \texttt{experiments/results/synthetic/synthetic\_pass\_observations.csv}
\end{itemize}
The geometry serves as the reference for all subsequent experiments.  Output
includes clean and noisy Doppler and delay series, carrier frequency, drift,
time offset, and noise levels---all recorded in the JSON metadata.

\subsection{Monte Carlo Coarse Localization Study}
The \texttt{run\_monte\_carlo\_synthetic.py} script runs repeated estimator
trials over the fixed synthetic geometry with independent noise realizations.
Each trial produces MAP location, error magnitude, posterior entropy, and HPD
region size.  Results are exported to:
\begin{itemize}
  \item \texttt{experiments/results/montecarlo/monte\_carlo\_trials.csv}
  \item \texttt{experiments/results/montecarlo/monte\_carlo\_summary.json}
\end{itemize}
The summary JSON records mean, median, p90 error magnitude, and posterior
entropy diagnostics.  These are \textbf{preliminary diagnostics only};
the number of trials (configurable via \texttt{--trials}) should be increased
for any published result, and confidence intervals must be reported.

\subsection{CRLB Timestamp Sensitivity Diagnostic}
The \texttt{diagnose\_crlb\_sensitivity.py} script evaluates the classical
CRLB lower bound across a sweep of timestamp noise $\sigma_\tau$.  Results are
exported to:
\begin{itemize}
  \item \texttt{experiments/results/crlb/crlb\_sensitivity.csv}
  \item \texttt{experiments/results/crlb/crlb\_sensitivity\_summary.json}
\end{itemize}
The sweep confirms that at $\sigma_\tau = 1$ ms (range noise $\approx 300$ km)
the CRLB for position exceeds several hundred km, establishing that sub-ms
timestamp accuracy is needed for meaningful range information.  The classical
CRLB assumes unbiased estimation with no priors on nuisance parameters; the
MAP estimator used in this work applies weak priors and is not directly
comparable to the classical CRLB.

\subsection{Trace-driven HIL Plan}
Section~\ref{sec:hil} describes the hardware-in-the-loop validation design
in detail.  No HIL runs have been executed; no real IQ captures are used in
this draft.  The plan specifies LR1121/STM32 as a characterized packet source
(transmit-only) and USRP B210 for IQ capture, with offline injection of
Doppler, CFO, delay, and noise.  The plan is trace-driven and makes no OTA
claims.

\subsection{Implemented Artifacts Summary}
\input{tables/evaluation_summary.tex}

\subsection{Reproduction Commands}
To regenerate all artifacts:
\begin{verbatim}
python scripts/generate_synthetic_dataset.py
python scripts/run_monte_carlo_synthetic.py --trials 5
python scripts/diagnose_crlb_sensitivity.py
python scripts/summarize_evaluation.py
\end{verbatim}

\textit{All results above are preliminary and synthetic.  No localization
accuracy claims are made.  No real satellite OTA validation is performed.}