\section{Conclusion}\label{sec:conclusion}

This paper has presented LEO-DTF: a model-driven framework for coarse
localization and uplink state estimation of direct-to-satellite IoT devices
using the Doppler-time fingerprint induced by LEO satellite motion.
By combining TLE-based orbit geometry (SGP4), a Doppler/range-rate observation
model, and a nuisance-aware Bayesian grid posterior estimator, the method
simultaneously infers the terminal's coarse position, time offset, CFO, and
oscillator drift from multi-observation pass data.

The current repository establishes: (i) the core algorithmic pipeline from
satellite geometry to posterior estimate; (ii) a reproducible synthetic-pass
evaluation framework with Monte Carlo diagnostics, CRLB sensitivity analysis,
and a Doppler-time ambiguity ablation study demonstrating the qualitative
value of multi-epoch fingerprints; (iii) a deterministic table and figure
generation pipeline; and (iv) a trace-driven HIL validation plan describing
the path from software simulation to hardware-in-the-loop verification
without over-the-air claims.

The manuscript is an early draft.  All quantitative results are currently
preliminary and synthetic.  Meter-level accuracy, real-satellite OTA
validation, and operational deployment are explicitly outside the current
scope and are not claimed.

Future work includes:
\begin{itemize}
  \item Completing the IQ Doppler injection and feature-extraction pipeline
        from LR1121/STM32 packet captures.
  \item Executing the trace-driven HIL validation with the USRP B210 front-end.
  \item Expanding the Monte Carlo evaluation with 100+ trials across diverse
        pass geometries and ROI configurations, with reported confidence
        intervals.
  \item Validating the full pipeline against an authorized OTA pass or a
        public D2S IoT dataset, if and when available.
  \item Integrating the estimator output with NTN uplink scheduling and
        link adaptation subsystems.
\end{itemize}

The repository is available at \url{https://github.com/Vanisherzd/LEO-DTF}
for reproducibility.
\end{section}